---
title: "Statistical Learning: ISLR Examples"
date: 2020-04-16
author: Kevin Z.
permalink: /posts/2020/04/ISLR/
output: ioslides_presentation
---


knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

# R Markdown Document

Maths expression embedded in GitHub Markdown:

$$
E = \frac{mc^2}{\sqrt{1-\frac{v^2}{c^2}}}
$$


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

summary(Credit)
lm(Balance ~ Student + Limit, data=Credit)

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

install.packages('ISLR')
library(ISLR)



